Trends of downward SDR in Thessaloniki 

### 2023-04-25 Article.Rmd
Commit 2023-04-25 15:17

Only data characterized as good quality were used in this study.
.....

@@

## Zenith angle dependance and years seasons.

@@

some data was rejected.......

@@

```{r trackercomm, echo=F, fig.cap="tracker"}
knitr::include_graphics("./images/LongtermTrends-2.pdf")
```

This is it \@ref(fig:trackercomm).

@@

<!-- \tiny -->
```{r echo=F}
pp <- data.table::fread("./figures/tbl_longterm_trends.dat")
pander::pander(pp,
               caption = "Table of trends and stats")
```
<!-- \normalsize -->

>>>>

....
Only data characterized as good quality were used in this study.
.....

@@

Using the mean daily Global radiation we produce the trends of each data set, as departure from the seasonal value.

```{r trendALL, echo=F, fig.cap="Daily Global radiation seasonal anomaly and long term trend, for all sky conditions."}
knitr::include_graphics("./images/LongtermTrends-2.pdf")
```

```{r trendCLEAR, echo=F, fig.cap="Daily Global radiation seasonal anomaly and long term trend, for clear sky conditions."}
knitr::include_graphics("./images/LongtermTrends-4.pdf")
```

```{r trendCLOUD, echo=F, fig.cap="Daily Global radiation seasonal anomaly and long term trend, for cloud sky conditions."}
knitr::include_graphics("./images/LongtermTrends-6.pdf")
```

## Zenith angle dependence and years seasons.

@@

@@

This is it \@ref(fig:trendALL).

@@

\tiny 
```{r echo=F}
pp <- data.table::fread("./figures/tbl_longterm_trends.dat")
pander::pander(pp,
               caption = "Table of trends and stats")
```
\normalsize

Some more text here
